Supplementary Material

### 2019-03-27 Paper/Supplement/Supplement.tex
Finished Updates from 3/18 Skype
Still need to look into refs we discussed, however
Added authors to supplement

\title{Supplementary Material}
\author{}

\renewcommand\Authands{ and }

>>>>

\title{Supplementary Material}
\author{Daniel R. Bergman$^{1}$,
Matthew Karikomi\,$^{1}$,
Qing Nie\,$^{1,2,*}$
and Adam L. MacLean\,$^{3,*}$
}
\affil{
  $^1$Department of Mathematics, University of California, Irvine,  Irvine, CA 92697, USA \\
  $^2$Department of Cell and Developmental Biology, University of California, Irvine, Irvine, CA 92697, USA \\
  $^3$Department of Biological Sciences, University of Southern California, Los Angeles, CA 90089, USA \\
  $^*$Correspondence:  qnie@uci.edu (QN); macleana@usc.edu (ALM).
}
\renewcommand\Authands{ and }

%\title{
%The competing effects of the immune system and EMT on epithelial cancers
%}

\date{}
